\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage{microtype}

\name{Tran Ngoc}{Duy}
\title{Business Analyst - Financial Services}
\address{Go Vap District, Ho Chi Minh City, Vietnam}
\phone[mobile]{0902866827}
\email{duytran82@gmail.com}
\social[linkedin]{duy-tran-4ab0b76}

\begin{document}

\makecvtitle

\section{Professional Summary \& Highlighted Achievements}
\cvitem{}{
    Experienced Business Analyst with over 15 years in the Banking and Financial sector, specializing in developing strategic IT solutions and transforming business operations. Expertise in requirement analysis, system documentation, and cross-functional team collaboration to enhance business processes and customer satisfaction.
    \begin{itemize}
        \item Requirement Analysis: Skilled in gathering and analyzing user requirements, preparing detailed business requirement specifications (BRS), and designing functional prototypes to meet business needs.
        \item Project Leadership: Led key initiatives, including the implementation of comprehensive CRM systems and integration projects within core banking systems, ensuring alignment with strategic business objectives.
        \item Team Collaboration \& Training: Proven track record in working effectively with development teams to ensure understanding and implementation of business requirements. Experienced in creating user manuals and conducting training sessions to enhance system adoption and utilization.
    \end{itemize}
}

\section{Experience \& Expertise}
\cventry{August 2018 -- January 2025}{Head of IT Department}{MIRAE ASSET Finance}{Vietnam}{}{
    \begin{itemize}
        \item Led the design and implementation of a company-wide CRM system, enhancing customer relationship management and operational efficiency.
        \item Collaborated with business stakeholders to define and document business processes and requirements, ensuring clear communication and alignment with development teams.
        \item Developed comprehensive system documentation and user manuals; conducted hands-on training sessions for system users.
    \end{itemize}
}
\cventry{June 2010 -- April 2018}{Business Analyst \& Developer}{ACB – Asia Commercial Bank}{Vietnam}{}{
    \begin{itemize}
        \item Played a pivotal role in the integration of Core Banking and HR systems, focusing on requirement gathering, system analysis, and solution design.
        \item Utilized tools like Visio and Balsamiq for creating wireframes and prototypes, facilitating effective communication of user requirements.
        \item Prepared detailed business analysis reports and presentations using Microsoft Office tools, enhancing project communication and stakeholder engagement.
    \end{itemize}
}
\cventry{January 2008 -- March 2010}{Vice Director}{Norske IT DA}{Norway}{}{
    Managed business operations with a focus on process optimization and financial management, contributing to strategic decision-making and business planning.
}
\cventry{October 2006 -- December 2007}{Software Developer}{Vestas Castings Group}{Norway}{}{
    Designed and implemented enterprise-level applications, focusing on user requirements and system efficiency.
}

\section{Education}
\cventry{2006--2011}{Master's Degree in Information Systems}{University of Agder}{Norway}{}{}
\cventry{2003--2006}{Bachelor's Degree in IT Administration \& Management}{University of Telemark}{Norway}{}{}

\section{Core Competencies}
\cvitem{Business Analysis}{Requirement Gathering, Business Requirement Documentation, Use Case Development, Wireframing (Visio, Balsamiq), Prototyping (Axure, Figma)}
\cvitem{Project Management \& Collaboration}{CRM Implementation, Cross-functional Team Leadership, Training \& Development, Stakeholder Engagement}
\cvitem{Technical Skills}{Microsoft Office Suite, Database Management (Oracle, MS SQL), Software Development (.Net, PHP, Java)}

\section{Languages}
\cvitemwithcomment{Vietnamese}{Native}{}
\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{Norwegian}{Fluent}{}

\end{document}