\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage{microtype}

\name{Tran Ngoc}{Duy}
\title{Senior IT Business Analyst}
\address{Go Vap District, Ho Chi Minh City, Vietnam}
\phone[mobile]{0902866827}
\email{duytran82@gmail.com}
\social[linkedin]{duy-tran-4ab0b76}

\begin{document}

\makecvtitle

\section{Professional Summary \& Highlighted Achievements}
\cvitem{}{
    Experienced IT Business Analyst with over 15 years of expertise in the Banking and Finance sector, specializing in requirement analysis, solution design, and quality assurance. Well-versed in managing complex IT projects, ensuring alignment with business needs and regulatory compliance.
    \begin{itemize}
        \item Proficient in gathering and clarifying functional and non-functional requirements, transforming them into comprehensive, traceable solution specifications for development teams.
        \item Skilled in designing and verifying functional designs, improving scalability, performance, and compliance with internal and industry regulations.
        \item Experienced in planning and executing quality testing strategies, including SIT, UAT, and regression testing, to ensure superior system performance and reliability.
        \item Effective in issue and risk management, identifying root causes, and implementing corrective actions to mitigate risks and ensure project compliance.
    \end{itemize}
}

\section{Experience \& Expertise}
\cventry{August 2018 -- Present}{Head of IT Department}{MIRAE ASSET Finance}{Vietnam}{}{
    \begin{itemize}
        \item Led the strategic planning and execution of IT projects, including the successful implementation of a company-wide CRM system, enhancing customer management and operational efficiency.
        \item Played a pivotal role in establishing IT policies and procedures, ensuring compliance and operational excellence.
        \item Managed and mentored the IT team, emphasizing professional development and high-performance standards.
    \end{itemize}
}
\cventry{June 2010 -- April 2018}{Development Team Member}{ACB – Asia Commercial Bank}{Vietnam}{}{
    \begin{itemize}
        \item Actively involved in the transformation of Core Banking and Core Card systems, ensuring they meet business requirements and regulatory standards.
        \item Implemented testing protocols for new systems, contributing to rigorous quality assurance processes.
        \item Utilized JIRA and Confluence for project management and documentation, ensuring effective team collaboration and project tracking.
    \end{itemize}
}
\cventry{January 2008 -- March 2010}{Vice Director}{Norske IT DA}{Norway}{}{
    Directed comprehensive business operations, including Process Management, Supply Chain Management, and Financial Oversight, to ensure efficient transaction processes.
}
\cventry{October 2006 -- December 2007}{Software Development Team Member}{Vestas Castings Group}{Norway}{}{
    Designed, developed, and deployed enterprise-level applications on the Windows Server platform.
}

\section{Education}
\cventry{2006--2011}{Master's Degree in Information Systems}{University of Agder}{Norway}{}{}
\cventry{2003--2006}{Bachelor's Degree in IT Administration \& Management}{University of Telemark}{Norway}{}{}

\section{Core Competencies}
\cvitem{Business Analysis \& Quality Assurance}{Expertise in Requirement Analysis, Solution Specification, Functional Design Verification, Test Planning and Execution, Risk Management}
\cvitem{Technology \& Tools}{Proficient in Core Banking Systems, CRM, JIRA, Confluence, Postman, Lucidchart, Draw.io, Bizagi}
\cvitem{Data Management \& Analysis}{Experienced in Database Development and Management, Data Analysis, and Reporting using Oracle and MS SQL}

\section{Languages}
\cvitemwithcomment{Vietnamese}{Native}{}
\cvitemwithcomment{English}{Fluent}{TOEIC score: 520}
\cvitemwithcomment{Norwegian}{Fluent}{}

\end{document}