\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage{microtype}

\name{Tran Ngoc}{Duy}
\title{Application Developer - Java and MIS Reporting Specialist}
\address{Go Vap District, Ho Chi Minh City, Vietnam}
\phone[mobile]{0902866827}
\email{duytran82@gmail.com}
\social[linkedin]{duy-tran-4ab0b76}

\begin{document}

\makecvtitle

\section{Professional Summary \& Highlighted Achievements}
\cvitem{}{
    Experienced Java Web Application Developer with over 15 years in IT, specializing in developing, maintaining, and supporting in-house IT systems and MIS reports for the banking sector. 
    \begin{itemize}
        \item Proficient in Java/J2EE, with a strong background in developing and optimizing web applications and integrating business data into actionable MIS reports.
        \item Demonstrated expertise in database management and application development using Oracle, MS SQL, and MySQL, with a focus on Java and .NET frameworks.
        \item Effective communicator and team collaborator who has successfully led IT projects and supported business requirements through sophisticated IT solutions.
    \end{itemize}
}

\section{Experience \& Expertise}
\cventry{June 2010 -- April 2018}{Development Team Member}{ACB – Asia Commercial Bank}{Vietnam}{}{
    \begin{itemize}
        \item Developed and maintained Java web applications and reporting tools, enhancing business processes and decision-making capabilities.
        \item Worked extensively with Java, .NET, Oracle, and MS SQL to create and optimize IT solutions.
        \item Played a key role in integrating and transforming IT systems, focusing on improving operational efficiencies and user experience.
    \end{itemize}
}
\cventry{August 2018 -- January 2025}{Head of IT Department}{MIRAE ASSET Finance}{Vietnam}{}{
    \begin{itemize}
        \item Led the development and implementation of a company-wide CRM system, incorporating Java and .NET technologies to streamline customer relationship management.
        \item Established IT strategies and policies that aligned with organizational objectives, significantly enhancing IT infrastructure and capabilities.
        \item Directed the IT team in developing and maintaining robust IT applications and systems, ensuring scalability and compliance.
    \end{itemize}
}
\cventry{October 2006 -- December 2007}{Software Development Team Member}{Vestas Castings Group}{Norway}{}{
    Designed, developed, and deployed enterprise-level applications on the Windows Server platform.
}
\cventry{January 2008 -- March 2010}{Vice Director}{Norske IT DA}{Norway}{}{
    Directed comprehensive business operations, including Process Management, Supply Chain Management, and Financial Oversight, to ensure efficient transaction processes.
}

\section{Education}
\cventry{2006--2011}{Master's Degree in Information Systems}{University of Agder}{Norway}{}{}
\cventry{2003--2006}{Bachelor's Degree in IT Administration \& Management}{University of Telemark}{Norway}{}{}

\section{Core Competencies}
\cvitem{Leadership \& Strategy}{IT Strategic Leadership, Project Management \& Implementation, Budget \& Resource Management}
\cvitem{Technology \& Systems}{Core System Management (Core Banking, Core Card), Customer Relationship Management (CRM), Software Development (.Net, PHP, Java, API)}
\cvitem{Data \& Analytics}{Data Warehouse Management, Data Analysis \& Reporting, Database Development (Oracle, MS SQL)}

\section{Languages}
\cvitemwithcomment{Vietnamese}{Native}{}
\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{Norwegian}{Fluent}{}

\end{document}