%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeSimpleEntry}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\\
    \end{tabular*}\vspace{-4pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\noindent
\textbf{\LARGE Tran Ngoc Duy} \\
\small +84 902 866 827 | \href{mailto:duytran82@gmail.com}{duytran82@gmail.com} | \href{https://www.linkedin.com/in/duy-tran-4ab0b76}{\myuline{LinkedIn}} | Go Vap District, HCMC
\vspace{10pt}

\vspace{4pt}
\noindent\small{Strategic IT Leadership expert with 15+ years of experience in technology vision, digital transformation, and operations in Banking \& Finance. Proven track record in leading enterprise-wide CRM/Core Banking implementations, building high-performance teams, and driving innovation. Strong combination of IT Strategy, Project Management, and Business Analysis expertise.}
\vspace{6pt}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {MIRAE ASSET Finance}{Ho Chi Minh City, Vietnam}
      {Head of IT Department}{Aug 2018 -- Jan 2025}
      \vspace{2pt}\\
      {\small\textit{Leading financial services company providing comprehensive financial solutions.}}
      \resumeItemListStart
        \resumeItem{Directed all IT operations, establishing and executing long-term Information Technology Strategy aligned with business objectives across the entire organization.}
        \resumeItem{Successfully implemented and operated company-wide CRM System, significantly enhancing customer experience and management efficiency.}
        \resumeItem{Developed, deployed, and operated Groupware system, digitizing company-wide business processes and improving operational efficiency.}
        \resumeItem{Built and standardized framework of IT Policies, Systems \& Processes, ensuring strict compliance and optimizing operational performance.}
        \resumeItem{Led recruitment, training, and development of IT team, fostering culture of professional growth and high-performance teamwork.}
        \resumeItem{Led R\&D initiatives and analyzed market trends to continuously improve systems and optimize operational efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {MIRAE ASSET Finance}{Ho Chi Minh City, Vietnam}
      {Deputy Manager}{Apr 2018 -- Jul 2018}
      \vspace{2pt}\\
      {\small\textit{Project Management and Business Analysis role.}}
      \resumeItemListStart
        \resumeItem{Managed strategic projects in PM and BA roles, including CRM System and Commission System implementations.}
        \resumeItem{Provided solutions to optimize business processes and improve operational efficiency across departments.}
      \resumeItemListEnd

    \resumeSubheading
      {ACB -- Asia Commercial Bank}{Vietnam}
      {Development Team Member}{Jun 2010 -- Apr 2018}
      \vspace{2pt}\\
      {\small\textit{Major commercial bank with comprehensive banking services.}}
      \resumeItemListStart
        \resumeItem{Key player in core system transformation projects including Core Banking DNA, Core Card, and Oracle PeopleSoft HR System integration.}
        \resumeItem{Developed enterprise applications using .Net, XML, PHP, PeopleCode, and related technologies.}
        \resumeItem{Designed and developed Oracle and MS SQL databases including tables, SQL scripts, functions, procedures, packages, views, and triggers.}
        \resumeItem{Provided project planning, resource management, and technical guidance, ensuring high-quality and on-time product delivery.}
        \resumeItem{Drove organizational transformation through successful core banking system integration and migration.}
      \resumeItemListEnd

    \resumeSubheading
      {Norske IT DA}{Norway}
      {Vice Director}{Jan 2008 -- Mar 2010}
      \vspace{2pt}\\
      {\small\textit{IT solutions and services company.}}
      \resumeItemListStart
        \resumeItem{Directed comprehensive business operations including Process Management, Supply Chain Management, and Financial Oversight.}
        \resumeItem{Ensured efficient transaction processes and operational excellence across all business units.}
      \resumeItemListEnd

    \resumeSubheading
      {Vestas Castings Group}{Norway}
      {Software Development Team Member}{Oct 2006 -- Dec 2007}
      \vspace{2pt}\\
      {\small\textit{Global leader in wind energy solutions.}}
      \resumeItemListStart
        \resumeItem{Designed, developed, and deployed enterprise-level applications on Windows Server platform.}
        \resumeItem{Collaborated with international teams to deliver high-quality software solutions for manufacturing operations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section {Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Agder}{2006 -- 2011}
      {Master's Degree in Information Systems}{Norway}
    \resumeSubheading
      {University of Telemark}{2003 -- 2006}
      {Bachelor's Degree in IT Administration \& Management}{Norway}
  \resumeSubHeadingListEnd


%
%-----------SKILLS-----------
\section{Core Competencies}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Leadership \& Strategy:} IT Strategic Leadership, Digital Transformation, Project Management, Business Analysis \\
     \textbf{Core Systems:} Core Banking Systems (DNA), Core Card Systems, CRM Platforms, Groupware Solutions \\
     \textbf{Enterprise Systems:} Oracle PeopleSoft HR, Business Process Management (BPM), Data Warehouse \\
     \textbf{Development:} .Net, Java, PHP, XML, PeopleCode, API Development \\
     \textbf{Databases:} Oracle, MS SQL Server (Tables, Procedures, Functions, Triggers, Views) \\
     \textbf{Management:} Team Leadership, Budget \& Resource Management, Contract Management, Policy Development \\
     \textbf{Analytics:} Data Analysis, Reporting, Business Intelligence \\
     \textbf{AI\&Automation:} Machine Learning (LLM,OpenAi), Robotic Process Automation (N8n, Make, Comfy), Intelligent Systems (OpenAi, Claude, VibeCoding) \\
     \textbf{Languages:} Vietnamese (Native), English (Fluent), Norwegian (Fluent) \\
     \textbf{Methodologies:} Agile, Waterfall, IT Governance, Risk Management, Compliance
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
