\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-1pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-1pt}\item\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ \textit{#3} & {\color{dark-grey} \small #4}\\\end{tabular*}\vspace{-4pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}#1 & {\color{dark-grey}} \\\end{tabular*}\vspace{-4pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSimpleEntry}[2]{\vspace{-1pt}\item\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & {\color{dark-grey}\small #2}\\\end{tabular*}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}
\color{text-grey}

\begin{document}

%----------HEADING----------
\noindent
\textbf{\LARGE Tran Ngoc Duy} \\
\small +84 902 866 827 | \href{mailto:duytran82@gmail.com}{duytran82@gmail.com} | \href{https://www.linkedin.com/in/duy-tran-4ab0b76}{\myuline{LinkedIn}} | Go Vap District, HCMC
\vspace{10pt}

\noindent\small{Business Analyst with a Master’s degree in Information Systems and over 12 years of experience in IT, specializing in business process analysis and system implementations in the Banking and Finance sectors. Proven expertise in translating complex business requirements into technical solutions, leading cross-functional teams, and delivering high-impact projects under tight deadlines.}
\vspace{6pt}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {MIRAE ASSET Finance}{Ho Chi Minh City, Vietnam}
      {Head of IT Department}{Aug 2018 -- Jan 2025}
      \resumeItemListStart
        \resumeItem{Spearheaded the implementation of system/applications aligned with business needs, including a CRM System that increased operational efficiency and customer satisfaction.}
        \resumeItem{Prepared comprehensive functional specifications and led system integration tests ensuring adherence to business requirements and quality standards.}
        \resumeItem{Managed mobile application development projects from concept through delivery, employing strong analytical skills to evaluate user requirements and propose effective solutions.}
        \resumeItem{Improved process flows and workflow efficiency by deploying groupware systems, enhancing team communication and project monitoring capabilities.}
      \resumeItemListEnd

    \resumeSubheading
      {ACB -- Asia Commercial Bank}{Vietnam}
      {Development Team Member}{Jun 2010 -- Apr 2018}
      \resumeItemListStart
        \resumeItem{Involved in user requirement gathering, SQL database design, and application development for core banking transformations, focusing on enhancing business operations.}
        \resumeItem{Contributed to user documentation and provided critical support during user acceptance testing phases.}
      \resumeItemListEnd

    \resumeSubheading
      {MIRAE ASSET Finance}{Ho Chi Minh City, Vietnam}
      {Deputy Manager}{Apr 2018 -- Jul 2018}
      \resumeItemListStart
        \resumeItem{Coordinated with technical teams to prepare proposals and evaluate vendor solutions, ensuring alignment with internal standards and business goals.}
      \resumeItemListEnd

    \resumeSubheading
      {Norske IT DA}{Norway}
      {Vice Director}{Jan 2008 -- Mar 2010}
      \resumeItemListStart
        \resumeItem{Directed operations and strategic projects, focusing on business analysis and system optimization for client services.}
      \resumeItemListEnd

    \resumeSubheading
      {Vestas Castings Group}{Norway}
      {Software Development Team Member}{Oct 2006 -- Dec 2007}
      \resumeItemListStart
        \resumeItem{Developed enterprise applications using .Net and SQL, improving manufacturing operations and data management.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section {Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Agder}{2006 -- 2011}
      {Master's Degree in Information Systems}{Norway}
    \resumeSubheading
      {University of Telemark}{2003 -- 2006}
      {Bachelor's Degree in IT Administration \& Management}{Norway}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Core Competencies}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Professional Skills:} Business Analysis, Project Management, System Implementation, User Requirements Gathering, SQL, Mobile App Development \\
     \textbf{Technologies:} iOS, Android, Progressive Web Applications, Oracle, MS SQL Server \\
     \textbf{Soft Skills:} Critical Thinking, Team Leadership, Communication, Negotiation, Design Thinking \\
     \textbf{Languages:} Vietnamese (Native), English (Fluent), Norwegian (Fluent)
    }}
 \end{itemize}

\end{document}