\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage{microtype}

\name{Tran Ngoc}{Duy}
\title{Product Development Manager}
\address{Go Vap District, Ho Chi Minh City, Vietnam}
\phone[mobile]{0902866827}
\email{duytran82@gmail.com}
\social[linkedin]{duy-tran-4ab0b76}

\begin{document}

\makecvtitle

\section{Professional Summary \& Highlighted Achievements}
\cvitem{}{
    Product Development Manager with over 15 years of experience in technology and business integration, specializing in cross-functional team leadership and product lifecycle management. Expert in aligning technology systems with business goals, enhancing product performance, and driving cross-domain collaboration.
    \begin{itemize}
        \item Effective in employing SAFe Agile Methodology to drive software development and operational efficiency.
        \item Demonstrated ability to work closely with Engineering, Finance, and Business Development teams to craft and execute strategic product plans.
        \item Skilled communicator adept at engaging with diverse professional groups to achieve business objectives.
    \end{itemize}
}

\section{Experience \& Expertise}
\cventry{August 2018 -- January 2025}{Head of IT Department}{MIRAE ASSET Finance}{Vietnam}{}{
    \begin{itemize}
        \item Led the strategic development and implementation of IT systems, including CRM, aligning with overall business goals and enhancing product performance.
        \item Fostered a collaborative team environment that encouraged cross-functional interaction between IT, Engineering, and Business Development.
        \item Applied SAFe Agile methodologies to optimize project delivery timelines and improve product life cycle management.
    \end{itemize}
}
\cventry{June 2010 -- April 2018}{Development Team Member}{ACB – Asia Commercial Bank}{Vietnam}{}{
    \begin{itemize}
        \item Integral in the development and transformation of core banking systems, utilizing .Net, PHP, and Java, ensuring robust product architectures.
        \item Collaborated with multi-disciplinary teams to design and develop scalable and efficient product solutions.
    \end{itemize}
}
\cventry{January 2008 -- March 2010}{Vice Director}{Norske IT DA}{Norway}{}{
    Managed business and technology integration, focusing on process efficiency and cross-domain collaboration in a multinational environment.
}
\cventry{October 2006 -- December 2007}{Software Development Team Member}{Vestas Castings Group}{Norway}{}{
    Developed enterprise-level applications, contributing to the foundational technology stack and supporting product design and architecture.
}

\section{Education}
\cventry{2006--2011}{Master's Degree in Information Systems}{University of Agder}{Norway}{}{}
\cventry{2003--2006}{Bachelor's Degree in IT Administration \& Management}{University of Telemark}{Norway}{}{}

\section{Core Competencies}
\cvitem{Leadership \& Strategy}{Cross-functional Team Leadership, Strategic Product Planning, SAFe Agile Methodology}
\cvitem{Technology \& Systems}{Product Lifecycle Management, CRM Systems, Software Development (.Net, PHP, Java)}
\cvitem{Data \& Analytics}{Engineering Architecture Understanding, Data Analysis \& Reporting, Database Development (Oracle, MS SQL)}

\section{Languages}
\cvitemwithcomment{Vietnamese}{Native}{}
\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{Norwegian}{Fluent}{}

\end{document}